---
title: "Homework 2"
author: "Tony Silva"
date: "January 25, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Number 1
Modules were read and watched

### Number 2

The below R code generates a 100X100 matrix where each column is a new sample of 100 from the Gaussian distribution, N(0,1). In the code, I take the average of each column which provides the individual estimates, x_bar_i. Next, I find the variance of each of the columns which provides the individual estimates, sigma_hat_i.

In the code, these are desribed by the variables, x_bars and sigma_hats. Both are vectors of size 100.
```{r}
set.seed(5)
# Create a 100x100 matrix, each column is a new iid N(0,1)
x <- matrix(ncol = 100, nrow=100)
for (i in 1:100) {
  x[,i] <- rnorm(100,0,1)
}

#Obtain the all the sample means and variances.
#colMeans takes mean of each column and puts it in a vector
#apply gets all the column variances.
#This is the x_bar_i
x_bars <- colMeans(x)
sigma_hats <- apply(x, 2, var)

# Mean and Variance of the averages from each of the 100 experiments taking 100 samples from N(0,1)
mean(x_bars)
var(x_bars)

# Mean and Variance of the variances from each of the 100 experiments taking 100 samples from N(0,1)
mean(sigma_hats)
var(sigma_hats)
```


From the above calculations we can see the average of all of the x_bars is very close to 0. Additionally, the variance of the all of the x_bars is extremly small as well. The average for all of the sigma_hats is extremely close to 1. The variance for these values is extremely small as well. This is makes sense because we pulled our samples from the Gaussian Distribution.

### Number 3
Let eps_t (Epsilon t) be the iid of N(0,1) for 1 <= t <= 500

We define sigma_t as follows.

```{r}
eps_t <- rnorm(500, 0,1)
```

Next, let's define x_t as x_t = eps_t + .5*eps_t-1
Assume, eps_t at t = 0 is 0.

```{r}
x_t <- vector(length=500)
for (i in 1:length(eps_t)) {
  if (i == 1) {
    x_t[i] <- eps_t[i]
  }else{
    x_t[i] <- eps_t[i] + .5*eps_t[i-1]
  }
}
```

We now have x_t. Now, we plot x_t vs. x_t-1, x_t-2, and t.

#### x_t vs. x_t-2
We can see the two lag plots below. The first is x_t vs. x_t-1. The second one is x_t vs. x_t-2
```{r}
lag.plot(x_t, lags=2)
```

From the first lag plot, it appears there is correlation between the current value of x_t vs. the previous value of x_t (t-1).

#### x_t vs. t
Now, we plot x_t across time. From the plot below we can see that there is not necessarily a trend. However, what is interesting is when points appear across time they generally appear with one other point close by. This could be the correlation we were seeing in the plot of x_t vs. x_t-1. 
```{r}
t <- 1:500
plot(x=t,y=x_t)
```

#### Mean, Variance, and Autocorrelation
Below is the average of x_t
```{r}
mean(x_t)
```

Below is the mean of x_t
```{r}
var(x_t)
```

Below is the autocorrelation of x_t and its plot
```{r}
acf(x_t, type = "correlation")
```

We can see from the Autocorrelation plot that x_t has a moderate correlation with its lag value of k=1. Which clarifies what we were seeing in the first plot and in the plot of x_t across t.

### Number 4

I created a new vector for each of the normally distributed random variables with their differing variance. I then combined them into a R data frame and plotted the variables on the same plot using reshape2 and ggplot2 packages. The names of the variables are associated with their variance measure. On the plot I used a different color for each of the variables.

You can see the plot below.
```{r}
library(reshape2)
library(ggplot2)
x_.1 <- rnorm(100,0,.1)
x_.5 <- rnorm(100,0,.5)
x_1 <- rnorm(100,0,1)
x_2 <- rnorm(100,0,2)
x_5 <- rnorm(100,0,5)

data <- as.data.frame(cbind(x_.1,x_.5,x_1,x_2,x_5))
data.m <- melt(data)
g<-ggplot(data.m, aes(value, color = variable)) + geom_density() 
g<- g+ggtitle("Plot of Multiple Normal Distributions with Different Variance")
g
```

From the plot, you can see as the variance increases the curve grows wider and wider. As the variance gets smaller the variance gets smaller and smaller.